### 2020-01-24 README.Rmd
fix links

- See richer examples the package [Tutorial](https://docs.ropensci.org/taxadb/articles/intro.html).

- Learn about the underlying data sources and formats in [Data Sources](https://docs.ropensci.org/taxadb/articles/articles/data-sources.html)

- Get better performance by selecting an alternative [database backend](https://docs.ropensci.org/taxadb/articles/articles/backends.html) engines.

>>>>

- See richer examples the package [Tutorial](https://docs.ropensci.org/taxadb/articles/articles/intro.html).

- Learn about the underlying data sources and formats in [Data Sources](https://docs.ropensci.org/taxadb/articles/data-sources.html)

- Get better performance by selecting an alternative [database backend](https://docs.ropensci.org/taxadb/articles/backends.html) engines.
